Demystifying the Combination of Dynamic Slicing and \\ Spectrum-based Fault Localization

### 2019-02-21 paper/ijcai/paper.tex
pass on intro

\begin{abstract}
Several approaches have been proposed in the literature to reduce
debugging costs through automated software fault diagnosis.  Dynamic
Slicing (\ds{}) and Spectrum-based Fault Localization (\sfl{}) are
popular fault diagnosis techniques and normally seen as complementary.
This paper reports on a comprehensive study\comments{--using
  \numFaults{} documented software faults from a credible dataset--}
to evaluate the effects of combining \ds{} with \sfl{}. We suspect
that several highly suspicious components---often involved in failing,
but seldom in passing test runs---may be unrelated to the bug. With
the aforementioned combination, such components could be located and
their suspiciousness reduced.  This study also discusses the practical
impact of the \ds{} key limitation---the risk of missing faulty
statements. Results indicate that \ds{} misses faulty statements in
only 9\%\comments{(23 misses)} of the 260 cases\Mar{we are using
  \numFaults{} in the paper. please, revise and use macros.} and that
the \ds{}-\sfl{} combination, coined as Tandem-SL, improves on average
the diagnostic accuracy by \Fix{Z} in 51\% of the cases. To sum, we
found that the \ds{}-\sfl{} combination was practical and effective
and encourage new \sfl{} techniques to be evaluated against that
optimization.
\end{abstract}

@@

\Mar{move this elsewhere...}
\Fix{
with the
goal of demystifying the impact of combining \ds{} with \sfl{}.

Despite tacit negative opinions of the research
community about the usefulness of \ds{} in automated debugging,}

Software debugging is important and challenging. In particular, the task of
locating the faulty code (\ie{}, fault localization) is particularly
challenging. For that reason, countless automated techniques have been proposed
in the past to reduce the cost of fault localization~\cite{7390282}.

Model-based software diagnosis (MBSD)~\cite{REITER198757,DEKLEER200325} and
Spectrum-Based Fault Localization (\sfl{}) are two very popular techniques that
leverage different principles to automate fault isolation. An example of a MBSD
is Dynamic Slicing (DS)~\cite{Agrawal:1990:DPS:93542.93576} as well as some
work~\cite{wotawa2002model,Mayer:2008:EMM:1642931.1642950,mayer2008prioritising,Perez:2018:LQR:3304889.3304927,Ko:2008:DRA:1368088.1368130},
a technique that traces back statements in the code that influence some point of
interest, such as the evaluation of a failing assertion. On the one hand, similarly to \ds{},
\sfl{} received tremendous attention in research over the years, but its
applicability to support debugging remains
questionable~\cite{ang-perez-van-deursen-rui-2017,Pearson:2017:EIF:3097368.3097441,Xie:2016:RAD:2884781.2884834}.
On the other hand, in contrast to \ds{},
\sfl{}~\cite{7390282} is instead a black-box,
statistical fault localization method that computes suspiciousness values
associated with program entities (e.g., methods) based on coverage information
gathered during the execution of test cases as well as the output of test cases.
More precisely, \sfl{} uses coverage information of passing and failing test
cases to identify likely faulty statements and produces on output a list of
program entities ranked in decreasing order of suspiciousness. \ds{} and \sfl{}
are complementary debugging techniques~\cite{DBLP:conf/sac/AbreuGZG08}.
Intuitively, \ds{} identifies irrelevant parts of the code whereas \sfl{} ranks
the relevant parts of the code.

@@

This paper reports the results of a a study using real-world applications to
evaluate the impact of combining \ds{} and \sfl{} to improve software fault
localization. We coin the toolset materializing this approach as \comb{}.  The
intuition for the combination is that several highly ranked statements, albeit
covered by failing executions, may be unrelated to the fault. Our empirical
study involves \numFaults{} faults from \numPrograms{} different programs
comprised in the Defects4J (D4J) dataset~\cite{just-defects4j-issta2014}, which
is frequently used to evaluate fault localization research. Prior work reported
promising results in this
combination~\cite{Wotawa:2010:FLB:1848650.1849235,Alves:2011:FUD:2190078.2190115,DBLP:conf/ecai/HoferW12,lei-mao-dai-wang-2012,slicing-sfl-repair},
but they used a non-representative set of subjects in their evaluation or used
archaic methods to evaluate technique
improvement~\cite{Wu:2014:CLC:2610384.2610386,Lucia:2014:FFL:2642937.2642983,Wen:2016:LLB:2970276.2970359}.

The goal of this paper is to reassess whether the \comb{} approach yields
promising results under a more rigorous experimental methodology and a larger
dataset.\comments{The D4J dataset is about twice as large than the biggest test
suite used in previous studies.} This study covers the following research
questions:

The first question addresses the important problem of missing faulty
statements. Naturally, the consequence of that problem for debugging
is that developers would never be able to locate faults. Different
slicers can miss faulty statements for different reasons. In this
paper, we used Critical Slicing~\cite{DeMillo:1996:CSS:229000.226310},
which, in principle, could miss statements because of imprecise
oracles that guide the slicing process. We evaluated how often that
issue manifests in our experiments. The second research questions
effectively evaluates the impact of the combination. Our
results show that the combination of the two approaches improves the accuracy
of fault localization of 51\% of the studied faults.

The contributions of this work are the following ones:
\begin{itemize}
	\item A study, using real-world applications and bugs, on the combination
    of \ds{} and \sfl{} for bug localization of \emph{Java} faulty programs.
   \item A tool that implements the combination of \ds{} with \sfl{}, coined
   \comb{}.
\end{itemize}

The tool as well as a replication package will be available once double-blind
requirements are lifted.

>>>>

\begin{abstract}
Several approaches have been proposed in the literature to reduce
debugging costs through automated software fault diagnosis.  Dynamic
Slicing (\ds{}) and Spectrum-based Fault Localization (\sfl{}) are
popular fault diagnosis techniques and normally seen as complementary.
This paper reports on a comprehensive study\comments{--using
  \numFaults{} documented software faults from a credible dataset--}
to evaluate the effects of combining \ds{} with \sfl{}. We suspect
that several highly suspicious components---often involved in failing,
but seldom in passing test runs---may be unrelated to the bug. With
the aforementioned combination, such components could be located and
their suspiciousness reduced.  This study also discusses the practical
impact of the \ds{} key limitation---the risk of missing faulty
statements. Results indicate that \ds{} misses faulty statements in
only 9\%\comments{(23 misses)} of the 260 cases\Mar{we are using
  \numFaults{} in the paper. please, revise and use macros.} and that
the \ds{}-\sfl{} combination, coined as Tandem-SL, improves on average
the diagnostic accuracy by \avgImprov\ in 51\% of the cases. To sum,
we found that the \ds{}-\sfl{} combination was practical and effective
and encourage new \sfl{} techniques to be evaluated against that
optimization.
\end{abstract}

@@

%% provide context (debugging + fault localization)
Software debugging is important and challenging. The task of locating
the faulty code (\ie{}, fault localization) is particularly
challenging. As such, countless automated techniques have been
proposed in the past to reduce the cost of fault
localization~\cite{7390282}. Model-based software diagnosis
(MBSD)~\cite{REITER198757,DEKLEER200325} and Spectrum-Based Fault
Localization (\sfl{})~\cite{DBLP:journals/stvr/HarroldRSWY00} are two
popular techniques that leverage different principles to automate
fault isolation~\cite{DBLP:conf/sac/AbreuGZG08}.  At a high-level,
MBSD
techniques~\cite{wotawa2002model,Mayer:2008:EMM:1642931.1642950,mayer2008prioritising,Perez:2018:LQR:3304889.3304927,Ko:2008:DRA:1368088.1368130}
attempt to eliminate non-suspicious components whereas \sfl{}
techniques attempt to rank suspicious components with the goal of
reducing fault diagnosis cost.

%% detail context (DS + SFL)
Dynamic Slicing (DS)~\cite{Agrawal:1990:DPS:93542.93576} is an
instance of MBSD that has attracted huge attention in research over
the last decades~\cite{Silva:2012:VPS:2187671.2187674}. The technique
traces back the statements in the code that influence a given point of
interest, such as the evaluation of a failing assertion.  Similarly to
\ds{}, \sfl{}~\cite{DBLP:journals/stvr/HarroldRSWY00} received
tremendous attention in research over the years~\cite{7390282}.  It
computes suspiciousness values associated with program components
(e.g., statements) based on coverage information gathered during the
execution of test cases.  More precisely, \sfl{} uses coverage
information of passing and failing test cases to identify likely
faulty statements and produces on output a list of program components
ranked in decreasing order of suspiciousness.

%% \ds{} and \sfl{} are complementary~\cite{DBLP:conf/sac/AbreuGZG08} and
%% could be combined.

Intuitively, \ds{} identifies irrelevant parts of the code (\ie{},
parts that do not contribute to the fault) whereas \sfl{} ranks the
relevant parts of the code. It is conceivable, therefore, to combine
these two techniques based on the intuition that highly ranked
statements (as per \sfl{}), albeit covered by failing executions,
could be in fact unrelated to the fault (as per \ds{}). In fact, prior
work reported promising preliminary results on this
combination~\cite{Wotawa:2010:FLB:1848650.1849235,Alves:2011:FUD:2190078.2190115,DBLP:conf/ecai/HoferW12,lei-mao-dai-wang-2012,slicing-sfl-repair}.
Unfortunately, they used a small set of subjects in their evaluation
or archaic---often optimistic---methods to evaluate fault localization
improvement~\cite{Wu:2014:CLC:2610384.2610386,Lucia:2014:FFL:2642937.2642983,Wen:2016:LLB:2970276.2970359}.

Given the importance of fault localization, this paper revisits the
problem of assessing the effectiveness of combining \ds{} and \sfl{},
addressing the issues from prior work. The study we conducted involves
\numFaults{}\Mar{check} faults from \numPrograms{}\Mar{check}
different programs from the Defects4J (D4J)
dataset~\cite{just-defects4j-issta2014}, which is frequently used to
evaluate fault localization research. The study covers the following
research questions:

%% The goal of this paper is to reassess whether the \comb{} approach yields
%% promising results under a more rigorous experimental methodology and a larger
%% dataset.\comments{The D4J dataset is about twice as large than the biggest test
%% suite used in previous studies.}

The first question addresses the problem that affects all dynamic
slicing techniques~\cite{Lin:2018:BDE:3238147.3238163}--that of
missing faulty statements. Naturally, the consequence of that problem
for debugging is that developers would never be able to locate
faults. Different slicers can miss faulty statements for different
reasons. In this paper, we used Critical
Slicing~\cite{DeMillo:1996:CSS:229000.226310}, which, in principle,
could miss statements because of imprecise oracles that guide the
slicing process.\comments{ We evaluated how often that issue manifests
  in our experiments.} The second research question evaluates the
impact of the combination. To sum, our results show that the
combination of the two approaches improves the accuracy of fault
localization on average by \avgImprov\ in 51\% of the studied faults.

The contributions of this work are: 1)~an empirical study, using
real-world applications and bugs, on the combination of \ds{} and
\sfl{} for bug localization of \emph{Java} faulty programs and 2)~a
tool that implements the combination of \ds{} with \sfl{}, coined
\comb{}.  The tool as well as a replication package will be available
once double-blind requirements are lifted.

%% -----------------
%% This paper reports the results of a comprehensive study to assess the
%% impact of combining two complementary techniques to improve software
%% fault localization.

%% It is worth noting that

%%  We
%% developed a tool, coined as \comb{}, materializing the
%% combination.

%% the research community manifests
%% explicit~\cite{ang-perez-van-deursen-rui-2017,Pearson:2017:EIF:3097368.3097441,Xie:2016:RAD:2884781.2884834}
%% or tacit negative opinions about the usefulness of \ds{} and \sfl{} in
%% automated debugging.
%% -----------------

%Dynamic Slicing~\cite{Agrawal:1990:DPS:93542.93576}------and \sfl{}.
%%% explain what each technique does (at a high level)

@@
